Efficient evaluation of threshold queries of derived fields in a numerical simulation database

### 2014-09-08 paper.tex
Discussion about most intense event

%Max vorticity clustering.
One of the applications of thresholding in turbulence is to find the locations of maximum vorticity in a particular time-step or the dataset as a whole.
The locations of maximum vorticity are usually associated with the most intense vortices in the dataset and often have interesting and complex
reconnection events associated with them. 
Once obtained from the service, these locations can be clustered in both 3d and 4d. This allows scientists to examine their evolution with the flow
and make subsequent analysis queries as needed in order to study these events.

@@

- 3d and 4d clusters of highest vorticity locations.

>>>>

%Max vorticity clustering.
One of the applications of thresholding in turbulence is to find the locations of maximum vorticity in a particular time-step or the dataset as a whole.
The locations of maximum vorticity are usually associated with the most intense vortices in the dataset and often have interesting and complex
reconnection events associated with them. 
Once obtained from the service, these locations can be clustered in both 3d and 4d. This allows scientists to examine their evolution with the flow
and make subsequent analysis queries as needed in order to study these events. The relationship between different worms that connect and reconnect
at those locations is of the most interest.

@@

Fig. \ref{fig:max_vort_cluster} shows the most intense event observed in the MHD dataset. The locations of maximum vorticity in the dataset were clustered
in this case in 4d using a friends-of-friends algorithm. It is interesting to note that the cluster containing the most intense event in the entire dataset develops
from nothing (i.e. it does not appear in the first few time-steps) and it takes less than the timespan stored in the database for it to develop. The timespan stored
is equal to about one large eddy turnover time. It is not clear whether a different more intense event could emerge from an existing cluster if the timespan stored
was larger. Fig. \ref{fig:max_vort_cluster} also shows that most interactions between worms are not simple. There are several worms interacting in a complex
way at the same time.
